### 2011-10-04 doc/manuscript.tex
The manuscript needs to be revised.

\subsubsection*{Version: 0.66 (Sep 30, 2011) \clearpage{}}

@@

%
\begin{table}
\caption{\label{tab:functional}Functional categories asscoiated with higher
recombination.}
\begin{tabular}{|c|c|c|}
\hline 
p-value & count & description\tabularnewline
\hline
\hline 
\multicolumn{3}{|c|}{\# Total number of recombinant edge types}\tabularnewline
\hline 
2.994e-07 &  28 & rRNA binding\tabularnewline
\hline 
1.447e-06 &  42 & structural constituent of ribosome\tabularnewline
\hline 
1.694e-05 &  39 & ribonucleoprotein complex\tabularnewline
\hline 
2.048e-05 &  23 & fatty acid biosynthetic process\tabularnewline
\hline 
3.664e-05 &  72 & ribosome\tabularnewline
\hline 
1.018e-04 &  86 & translation\tabularnewline
\hline 
1.733e-04 &  22 & lipid biosynthetic process\tabularnewline
\hline 
2.792e-04 & 108 & RNA binding\tabularnewline
\hline 
4.164e-04 &  47 & carbohydrate transport\tabularnewline
\hline 
1.303e-03 &  38 & phosphoenolpyruvate-dependent sugar phosphotransferase 
system\tabularnewline
\hline 
1.345e-03 &  10 & pentose-phosphate shunt\tabularnewline
\hline 
1.819e-03 &  35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase 
activity\tabularnewline
\hline 
\multicolumn{3}{|c|}{\# SDE->SPY recombinant edge types}\tabularnewline
\hline 
0.0001236 & 28 & rRNA binding\tabularnewline
\hline 
0.0001284 & 86 & translation\tabularnewline
\hline 
0.0001711 & 39 & ribonucleoprotein complex\tabularnewline
\hline 
0.0002230 & 10 & pentose-phosphate shunt\tabularnewline
\hline 
0.0003412 & 38 & phosphoenolpyruvate-dependent sugar phosphotransferase 
system\tabularnewline
\hline 
0.0004498 & 42 & structural constituent of ribosome\tabularnewline
\hline 
0.0007789 & 47 & carbohydrate transport\tabularnewline
\hline 
0.0008152 & 35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase 
activity\tabularnewline
\hline 
\multicolumn{3}{|c|}{\# SPY->SDE recombinant edge types}\tabularnewline
\hline 
2.025e-06 & 47 & carbohydrate transport\tabularnewline
\hline 
1.875e-04 & 38 & phosphoenolpyruvate-dependent sugar phosphotransferase 
system\tabularnewline
\hline 
2.843e-04 & 18 & sodium ion transport\tabularnewline
\hline 
3.248e-04 & 35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase 
activity\tabularnewline
\hline
\end{tabular}

\end{table}

\clearpage{}%

% Table 2. 
\begin{table}
\caption{\label{tab:go-events}
GO-term enrichment for different evolutionary events. }

\begin{tabular}{rrll}
P-value & Count & GO-term & Description \\
\hline
\multicolumn{4}{c}{Duplications} \\
\hline
4e-81 &  67 & GO:0006313 & transposition, DNA-mediated\\
5e-80 &  59 & GO:0004803 & transposase activity\\
6e-70 &  23 & GO:0032196 & transposition\\
2e-58 &  52 & GO:0015074 & DNA integration\\
8e-25 &  86 & GO:0006310 & DNA recombination\\
1e-20 &  36 & GO:0016987 & sigma factor activity\\
1e-20 &  36 & GO:0006352 & transcription initiation\\
2e-19 & 197 & GO:0003676 & nucleic acid binding\\
2e-10 & 527 & GO:0003677 & DNA binding\\
4e-06 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline
\hline
\multicolumn{4}{c}{Losses} \\
\hline
1e-06 &  67 & GO:0006313 & transposition, DNA-mediated\\
2e-05 &  59 & GO:0004803 & transposase activity\\
5e-05 &  52 & GO:0015074 & DNA integration\\
5e-04 &  23 & GO:0032196 & transposition\\
5e-04 &  10 & GO:0046873 & metal ion transmembrane transporter activity\\
7e-04 &  36 & GO:0016987 & sigma factor activity\\
7e-04 &  36 & GO:0006352 & transcription initiation\\
1e-03 &  31 & GO:0006814 & sodium ion transport\\
3e-03 &  86 & GO:0006310 & DNA recombination\\
6e-03 & 197 & GO:0003676 & nucleic acid binding\\
\hline
\hline
\multicolumn{4}{c}{Non-recombining transfers} \\
\hline
7e-61 &  67 & GO:0006313 & transposition, DNA-mediated\\
3e-58 &  59 & GO:0004803 & transposase activity\\
1e-30 &  52 & GO:0015074 & DNA integration\\
1e-28 &  23 & GO:0032196 & transposition\\
1e-13 & 527 & GO:0003677 & DNA binding\\
2e-12 &  86 & GO:0006310 & DNA recombination\\
1e-11 & 197 & GO:0003676 & nucleic acid binding\\
3e-09 &  36 & GO:0016987 & sigma factor activity\\
3e-09 &  36 & GO:0006352 & transcription initiation\\
3e-08 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline
\hline
\multicolumn{4}{c}{Recombining transfers} \\
\hline
7e-09 & 153 & GO:0006412 & translation\\
1e-08 &  67 & GO:0030529 & ribonucleoprotein complex\\
1e-07 &  45 & GO:0019843 & rRNA binding\\
2e-06 &  73 & GO:0003735 & structural constituent of ribosome\\
3e-05 & 157 & GO:0005840 & ribosome\\
7e-05 & 221 & GO:0003723 & RNA binding\\
2e-04 &  11 & GO:0004826 & phenylalanine-tRNA ligase activity\\
3e-04 &  14 & GO:0015413 & nickel-transporting ATPase activity\\
4e-04 &  93 & GO:0008982 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\\
5e-04 & 104 & GO:0009401 & phosphoenolpyruvate-dependent sugar phosphotransferase system\\
\end{tabular}

\end{table}

@@

%=============================================================================
% FIGURE 2. - Transfer heatmap
\begin{figure}
\begin{center}
% \includegraphics[width=5in]{figures/trans-hgt-heatmap}
\includegraphics[width=5in]{figures/heatmap-hgtedge}
\end{center}
\vspace{-1.2in}
\caption{Distribution of horizontal gene transfers.}
\label{fig:hgt-heatmap}
\end{figure}
%=============================================================================

@@

%=============================================================================
% Table S4. The values of the heat map.
\begin{table}
\caption{\label{tab:heatmap}}
\noindent \centering{}\begin{tabular}{ccccccccc}
\hline
& SDE1 & SDE & SDE2 & SD & SDD & ROOT & SPY1 & SPY & SPY2\tabularnewline
\hline
SDE1& 0.176  &   NA  &1.170  &    NA & 0.7564  & NA & 0.67 &    NA & 0.663\tabularnewline
SDE & -0.118 & 0.081 &-0.202 &     NA&  0.3395 &  NA& -0.15&  0.045& -0.323\tabularnewline
SDE2& 1.201  &   NA  &0.092  &    NA & 0.6978  & NA & 0.60 &    NA & 0.387\tabularnewline
SD  & -0.629 & 0.022 &-0.661 &0.00670&  0.0078 &  NA& -0.94& -0.299& -1.030\tabularnewline
SDD & -0.317 & 0.371 &-0.197 &     NA&  0.0752 &  NA& -1.06& -0.525& -0.915\tabularnewline
ROOT& -1.745 &-0.698 &-1.786 &0.23039& -0.4854 &  NA& -1.37&  0.497& -1.306\tabularnewline
SPY1& 1.245  &1.883  &1.251  &    NA &-2.1997  & NA & 0.06 &    NA & 1.062\tabularnewline
SPY & 0.089  &0.200  &0.298 &0.00098 &-0.7903  & NA &-0.19 &-0.058 &-0.159\tabularnewline
SPY2& 1.174  &1.938  &1.287  &    NA &-1.9740  & NA & 1.07 &    NA & 0.063\tabularnewline
\hline
\end{tabular}
\end{table}
\clearpage{}
%=============================================================================

%=============================================================================
% Table S5. The values of the heat map of actual counts.
\begin{table}
\caption{\label{tab:obsheatmap}}
\noindent \centering{}\begin{tabular}{ccccccccc}
\hline
& SDE1 & SDE & SDE2 & SD & SDD & ROOT & SPY1 & SPY & SPY2\tabularnewline
\hline
SDE1&8.896 &  0.00 &17.712  & 0.00 & 12.872   & 0 &12.59  &  0.00  &12.53\tabularnewline
SDE &44.626& 136.49& 42.088 &  0.00& 227.061  &  0& 73.39 &  99.95 & 65.25\tabularnewline
SDE2&18.099&   0.00&  8.393 &  0.00&  12.360  &  0& 11.97 &   0.00 & 10.36\tabularnewline
SD  &9.671 &101.74 & 9.464  &31.26 &115.796   & 0 &13.68  & 98.38  &12.86\tabularnewline
SDD &45.539& 168.58& 49.513 &  0.00& 194.706  &  0& 43.09 &  67.14 & 47.65\tabularnewline
ROOT&43.553& 602.67& 42.337 &765.53& 802.813  &  0& 98.86 &2146.01 &103.60\tabularnewline
SPY1&40.800&  11.46& 40.973 &  0.00&   4.371  &  0& 21.15 &   0.00 & 42.35\tabularnewline
SPY &57.618& 262.08& 66.594 & 30.92& 163.518  &  0& 83.56 & 207.00 & 85.10\tabularnewline
SPY2&38.837&  11.90& 42.000 &  0.00&   5.111  &  0& 42.45 &   0.00 & 21.19\tabularnewline
\hline
\end{tabular}
\end{table}
\clearpage{}
%=============================================================================

%=============================================================================
% Table SXXX. Simulation study for the three population parameters.
\begin{table}
\caption{\label{tab:sim-three-population-parameters}
Simulation study of the three population parameters.}
\noindent \begin{centering}
\begin{tabular}{ccc}
 & True & Estimates (Standard Deviation)\tabularnewline
\hline
Mutation rate per site & 0.081 & 0.081 (0.0011)\tabularnewline
Recombination rate per site & 0.012 & 0.011 (0.0003)\tabularnewline
Recombinant tract length & 744 bp & 919 bp (28)\tabularnewline
\end{tabular}
\par\end{centering}
\end{table}
\clearpage{}
%=============================================================================

% Table S1. Gene Tree topologies
\begin{table}
\caption{\label{tab:Gene-tree-topologies}Posterior probability of gene tree
topologies.}
\begin{tabular}{|c|c|}
\hline 
Gene tree topologies & Posterior probability\tabularnewline
\hline
\hline 
(((SDE1,SDE2),SDD),(SPY1,SPY2)) & 66.7\%\tabularnewline
\hline 
(((SDE1,SDE2),(SPY1,SPY2)),SDD) & 9.3\%\tabularnewline
\hline 
((SDE1,SDE2),(SDD,(SPY1,SPY2))) & 3.5\%\tabularnewline
\hline 
(((SDE1,(SDE2,SDD)),(SPY1,SPY2)) & 1.5\%\tabularnewline
\hline 
(((SDE1,SDD),SDE2),(SPY1,SPY2)) & 1.3\%\tabularnewline
\hline 
((SDE1,SDD),(SDE2,(SPY1,SPY2))) & 1.2\%\tabularnewline
\hline 
((((SDE1,SDE2),SPY1),SPY2),SDD) & 1.0\%\tabularnewline
\hline 
((SDE2,SDD),(SDE1,(SPY1,SPY2))) & 1.0\%\tabularnewline
\hline
\end{tabular}
\end{table}
\clearpage{}

@@

\begin{tabular}{|lllllll|}

@@

@@

%=============================================================================
% Figure S1: Mauve alignment
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/mauve.pdf}
\end{center}
\vspace{-1.2in}
\caption{Alignment of the five genomes.}
\label{fig:mauve}
\end{figure}
\clearpage{}
%=============================================================================

@@

%=============================================================================
% Figure S5. A Recombinant Tree of ClonalOrigin Model
\begin{figure}
\includegraphics[scale=0.42]{figures/mauve-analysis-001}
\caption{\label{fig:clonalorigin}Recombinant tree in the \texttt{ClonalOrigin} model.
(A) A recombinant tree relating the five genomes with three recombinant edges.
(B) A genomic region of size 100 base pairs with subregions affected by the
three recombinant edges. Genomic positions are evenly marked by ticks every 
10-th base pair. Local gene trees induced by the recombinant tree are
illustrated for each region covered by some combinations of recombinant edges
along the genomic region (C-G). For example, the local gene tree (E) is created
by all of the three recombinant edges in the subregion between 51 base pairs
and 70 base pairs.

We first describe procedures of summarizing recombinant trees from the first
viewpoint.  To summarize the posterior samples of \texttt{ClonalOrigin} we
examined the distribution of topologies of local genealogies induced by the
sampled recombinant trees. Recall that a recombinant tree induces a local
genealogy for each site along the analyzed block.  Figure \ref{fig:clonalorigin}
shows six local gene trees including one that is the same as the species tree
from the most left-hand side of the block of 100 base pairs to the right.  We
expected the dominant topology across sampled genealogies to be concordant with
that of the species tree. However, other frequently sampled topologies were
expected to be potentially informative about common recombination events. There
are 105 possible rooted topologies relating five taxa, which allowed us to count
topologies induced by a posterior sample of recombinant trees.

For the second viewpoint of recombinant trees \citet{Didelot2010} suggested an
approach used to trace recombination intensity along the genome.  For each edge
type and each site, we recorded the sampling frequency of a recombinant edge of
the type at that site (e.g., Figure S\ref{fig:muts}).  Figure
\ref{fig:clonalorigin}B illustrates the posterior probability that a site
experiences influx from a donor branch using a single recombinant tree.  Summing
these posteriors over a certain set of edge types, we could obtain a measure of
recombination intensity along the genome (Figure \ref{fig:clonalorigin}B).

}
\end{figure}
%=============================================================================

%=============================================================================
% Figure S6: View of UCSC genome browser for bacterial gene transfer.
\begin{figure}
\includegraphics[scale=0.6]{figures/ucsc}
\caption{\label{fig:muts}Posterior probability of recombinant edges on 
aspartyl-tRNA
synthetase.  The
top line represents a genomic location of the current view in SPY1 genome. Locus
tags are represented below. The start of a locus tag is red colored, and the end
blue colored. Each of nine horizontal bars represents a branch of the five
species tree. The species tree branch is a recipient species.
The red area on SDE1 line represents gene fragment transfer from
SPY1 due to recombination in locus SpyM3\_1814 of aspartyl-tRNA synthetase.}
\end{figure}
\clearpage{}%
%=============================================================================

@@

%=============================================================================
% Figure S9:
\begin{figure}
\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R}}
\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R-inset}}
\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R-inset2}}

@@

% Figure S8: recombination heatmap from mowgli
%=============================================================================
% FIGURE - Transfer heatmap
\begin{figure}
\begin{center}
% \includegraphics[width=5in]{figures/trans-recomb-heatmap}
\includegraphics[width=5in]{figures/heatmap-recedge-mowgli}
\end{center}
\vspace{-1.2in}
\caption{Distribution of recombining horizontal gene transfers.}
\label{fig:mowgli-recomb-heatmap}
\end{figure}
\clearpage{}
%=============================================================================

>>>>

\subsubsection*{Version: 0.67 (Oct 7, 2011) \clearpage{}}

@@

%
\begin{table}
\caption{\label{tab:functional}Functional categories asscoiated with higher
recombination - Total number of recombinant edge types.}
\begin{tabular}{ccc}
\hline 
p-value & count & description\tabularnewline
\hline 
2.994e-07 &  28 & rRNA binding\tabularnewline
1.447e-06 &  42 & structural constituent of ribosome\tabularnewline
1.694e-05 &  39 & ribonucleoprotein complex\tabularnewline
2.048e-05 &  23 & fatty acid biosynthetic process\tabularnewline
3.664e-05 &  72 & ribosome\tabularnewline
1.018e-04 &  86 & translation\tabularnewline
1.733e-04 &  22 & lipid biosynthetic process\tabularnewline
2.792e-04 & 108 & RNA binding\tabularnewline
4.164e-04 &  47 & carbohydrate transport\tabularnewline
1.303e-03 &  38 & phosphoenolpyruvate-dependent sugar phosphotransferase system\tabularnewline
1.345e-03 &  10 & pentose-phosphate shunt\tabularnewline
1.819e-03 &  35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\tabularnewline
\hline 
\end{tabular}
\end{table}
\clearpage{}

%
\begin{table}
\caption{\label{tab:go-events}GO-term enrichment for different
evolutionary events - Non-recombining transfers.}
\begin{tabular}{cccc}
\hline 
P-value & Count & GO-term & Description \\
\hline 
7e-61 &  67 & GO:0006313 & transposition, DNA-mediated\\
3e-58 &  59 & GO:0004803 & transposase activity\\
1e-30 &  52 & GO:0015074 & DNA integration\\
1e-28 &  23 & GO:0032196 & transposition\\
1e-13 & 527 & GO:0003677 & DNA binding\\
2e-12 &  86 & GO:0006310 & DNA recombination\\
1e-11 & 197 & GO:0003676 & nucleic acid binding\\
3e-09 &  36 & GO:0016987 & sigma factor activity\\
3e-09 &  36 & GO:0006352 & transcription initiation\\
3e-08 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline 
\end{tabular}
\end{table}
\clearpage{}

@@

%=============================================================================
% FIGURE 2. - HGT Transfer heatmap
\begin{figure}
\begin{center}
% \includegraphics[width=5in]{figures/trans-hgt-heatmap}
\includegraphics[scale=0.45]{figures/heatmap-hgtedge}
\end{center}
\caption{Distribution of horizontal gene transfers.}
\label{fig:hgt-heatmap}
\end{figure}
\clearpage{}%
%=============================================================================

@@

%=============================================================================
% Table S4. The values of the heat map.
\begin{table}
\caption{\label{tab:heatmap}}
\noindent \centering{}\begin{tabular}{cccccccccc}
\hline
& SDE1 & SDE & SDE2 & SD & SDD & ROOT & SPY1 & SPY & SPY2 \tabularnewline
\hline
SDE1& 0.176  &   NA  &1.170  &    NA & 0.7564  & NA & 0.67 &    NA & 0.663\tabularnewline
SDE & -0.118 & 0.081 &-0.202 &     NA&  0.3395 &  NA& -0.15&  0.045& -0.323\tabularnewline
SDE2& 1.201  &   NA  &0.092  &    NA & 0.6978  & NA & 0.60 &    NA & 0.387\tabularnewline
SD  & -0.629 & 0.022 &-0.661 &0.00670&  0.0078 &  NA& -0.94& -0.299& -1.030\tabularnewline
SDD & -0.317 & 0.371 &-0.197 &     NA&  0.0752 &  NA& -1.06& -0.525& -0.915\tabularnewline
ROOT& -1.745 &-0.698 &-1.786 &0.23039& -0.4854 &  NA& -1.37&  0.497& -1.306\tabularnewline
SPY1& 1.245  &1.883  &1.251  &    NA &-2.1997  & NA & 0.06 &    NA & 1.062\tabularnewline
SPY & 0.089  &0.200  &0.298 &0.00098 &-0.7903  & NA &-0.19 &-0.058 &-0.159\tabularnewline
SPY2& 1.174  &1.938  &1.287  &    NA &-1.9740  & NA & 1.07 &    NA & 0.063\tabularnewline
\hline
\end{tabular}
\end{table}
\clearpage{}
%=============================================================================

%=============================================================================
% Table S5. The values of the heat map of actual counts.
\begin{table}
\caption{\label{tab:obsheatmap}}
\noindent \centering{}\begin{tabular}{cccccccccc}
\hline
& SDE1 & SDE & SDE2 & SD & SDD & ROOT & SPY1 & SPY & SPY2 \tabularnewline
\hline
SDE1&8.896 &  0.00 &17.712  & 0.00 & 12.872   & 0 &12.59  &  0.00  &12.53\tabularnewline
SDE &44.626& 136.49& 42.088 &  0.00& 227.061  &  0& 73.39 &  99.95 & 65.25\tabularnewline
SDE2&18.099&   0.00&  8.393 &  0.00&  12.360  &  0& 11.97 &   0.00 & 10.36\tabularnewline
SD  &9.671 &101.74 & 9.464  &31.26 &115.796   & 0 &13.68  & 98.38  &12.86\tabularnewline
SDD &45.539& 168.58& 49.513 &  0.00& 194.706  &  0& 43.09 &  67.14 & 47.65\tabularnewline
ROOT&43.553& 602.67& 42.337 &765.53& 802.813  &  0& 98.86 &2146.01 &103.60\tabularnewline
SPY1&40.800&  11.46& 40.973 &  0.00&   4.371  &  0& 21.15 &   0.00 & 42.35\tabularnewline
SPY &57.618& 262.08& 66.594 & 30.92& 163.518  &  0& 83.56 & 207.00 & 85.10\tabularnewline
SPY2&38.837&  11.90& 42.000 &  0.00&   5.111  &  0& 42.45 &   0.00 & 21.19\tabularnewline
\hline
\end{tabular}
\end{table}
\clearpage{}
%=============================================================================

%=============================================================================
% Table SXXX. Simulation study for the three population parameters.
\begin{table}
\caption{\label{tab:sim-three-population-parameters}
Simulation study of the three population parameters.}
\noindent \begin{centering}
\begin{tabular}{ccc}
 & True & Estimates (Standard Deviation)\tabularnewline
\hline
Mutation rate per site & 0.081 & 0.081 (0.0011)\tabularnewline
Recombination rate per site & 0.012 & 0.011 (0.0003)\tabularnewline
Recombinant tract length & 744 bp & 919 bp (28)\tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}
\clearpage{}
%=============================================================================

% Table S1. Gene Tree topologies
\begin{table}
\caption{\label{tab:Gene-tree-topologies}Posterior probability of gene tree
topologies.}
\noindent \begin{centering}
\begin{tabular}{cc}
\hline 
Gene tree topologies & Posterior probability\tabularnewline
\hline
(((SDE1,SDE2),SDD),(SPY1,SPY2)) & 66.7\%\tabularnewline
(((SDE1,SDE2),(SPY1,SPY2)),SDD) & 9.3\%\tabularnewline
((SDE1,SDE2),(SDD,(SPY1,SPY2))) & 3.5\%\tabularnewline
(((SDE1,(SDE2,SDD)),(SPY1,SPY2)) & 1.5\%\tabularnewline
(((SDE1,SDD),SDE2),(SPY1,SPY2)) & 1.3\%\tabularnewline
((SDE1,SDD),(SDE2,(SPY1,SPY2))) & 1.2\%\tabularnewline
((((SDE1,SDE2),SPY1),SPY2),SDD) & 1.0\%\tabularnewline
((SDE2,SDD),(SDE1,(SPY1,SPY2))) & 1.0\%\tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}
\clearpage{}

@@

\begin{tabular}{lllllll}

@@

%
\begin{table}
\caption{\label{tab:functional-sde-spy}Functional categories asscoiated with higher
recombination - \# SDE->SPY recombinant edge types.}
\begin{tabular}{ccc}
\hline 
p-value & count & description\tabularnewline
\hline 
0.0001236 & 28 & rRNA binding\tabularnewline
0.0001284 & 86 & translation\tabularnewline
0.0001711 & 39 & ribonucleoprotein complex\tabularnewline
0.0002230 & 10 & pentose-phosphate shunt\tabularnewline
0.0003412 & 38 & phosphoenolpyruvate-dependent sugar phosphotransferase system\tabularnewline
0.0004498 & 42 & structural constituent of ribosome\tabularnewline
0.0007789 & 47 & carbohydrate transport\tabularnewline
0.0008152 & 35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\tabularnewline
\hline 
\end{tabular}
\end{table}
\clearpage{}

%
\begin{table}
\caption{\label{tab:functional-spy-sde}Functional categories asscoiated with higher
recombination - \# SPY->SDE recombinant edge types.}
\begin{tabular}{ccc}
\hline 
p-value & count & description\tabularnewline
\hline 
2.025e-06 & 47 & carbohydrate transport\tabularnewline
1.875e-04 & 38 & phosphoenolpyruvate-dependent sugar phosphotransferase system\tabularnewline
2.843e-04 & 18 & sodium ion transport\tabularnewline
3.248e-04 & 35 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\tabularnewline
\hline 
\end{tabular}
\end{table}
\clearpage{}

%
\begin{table}
\caption{\label{tab:go-events}GO-term enrichment for different
evolutionary events - Duplication.}
\begin{tabular}{cccc}
\hline 
P-value & Count & GO-term & Description \\
\hline 
4e-81 &  67 & GO:0006313 & transposition, DNA-mediated\\
5e-80 &  59 & GO:0004803 & transposase activity\\
6e-70 &  23 & GO:0032196 & transposition\\
2e-58 &  52 & GO:0015074 & DNA integration\\
8e-25 &  86 & GO:0006310 & DNA recombination\\
1e-20 &  36 & GO:0016987 & sigma factor activity\\
1e-20 &  36 & GO:0006352 & transcription initiation\\
2e-19 & 197 & GO:0003676 & nucleic acid binding\\
2e-10 & 527 & GO:0003677 & DNA binding\\
4e-06 & 142 & GO:0043565 & sequence-specific DNA binding\\
\hline 
\end{tabular}
\end{table}
\clearpage{}

%
\begin{table}
\caption{\label{tab:go-events}GO-term enrichment for different
evolutionary events - Loss.}
\begin{tabular}{cccc}
\hline 
P-value & Count & GO-term & Description \\
\hline 
1e-06 &  67 & GO:0006313 & transposition, DNA-mediated\\
2e-05 &  59 & GO:0004803 & transposase activity\\
5e-05 &  52 & GO:0015074 & DNA integration\\
5e-04 &  23 & GO:0032196 & transposition\\
5e-04 &  10 & GO:0046873 & metal ion transmembrane transporter activity\\
7e-04 &  36 & GO:0016987 & sigma factor activity\\
7e-04 &  36 & GO:0006352 & transcription initiation\\
1e-03 &  31 & GO:0006814 & sodium ion transport\\
3e-03 &  86 & GO:0006310 & DNA recombination\\
6e-03 & 197 & GO:0003676 & nucleic acid binding\\
\hline 
\end{tabular}
\end{table}
\clearpage{}

%
\begin{table}
\caption{\label{tab:go-events}GO-term enrichment for different
evolutionary events - Recombining transfers.}
\begin{tabular}{cccc}
\hline 
P-value & Count & GO-term & Description \\
\hline 
7e-09 & 153 & GO:0006412 & translation\\
1e-08 &  67 & GO:0030529 & ribonucleoprotein complex\\
1e-07 &  45 & GO:0019843 & rRNA binding\\
2e-06 &  73 & GO:0003735 & structural constituent of ribosome\\
3e-05 & 157 & GO:0005840 & ribosome\\
7e-05 & 221 & GO:0003723 & RNA binding\\
2e-04 &  11 & GO:0004826 & phenylalanine-tRNA ligase activity\\
3e-04 &  14 & GO:0015413 & nickel-transporting ATPase activity\\
4e-04 &  93 & GO:0008982 & protein-N(PI)-phosphohistidine-sugar phosphotransferase activity\\
5e-04 & 104 & GO:0009401 & phosphoenolpyruvate-dependent sugar phosphotransferase system\\
\hline 
\end{tabular}
\end{table}
\clearpage{}

@@

%=============================================================================
% Figure S1: Mauve alignment
\begin{figure}
\begin{center}
\includegraphics[scale=0.2]{figures/mauve}
\end{center}
\caption{Alignment of the five genomes.}
\label{fig:mauve}
\end{figure}
\clearpage{}
%=============================================================================

@@

%=============================================================================
% Figure S5. A Recombinant Tree of ClonalOrigin Model
\begin{figure}
\includegraphics[scale=0.42]{figures/mauve-analysis-001}
\caption{\label{fig:clonalorigin}Recombinant tree in the \texttt{ClonalOrigin} model.
(A) A recombinant tree relating the five genomes with three recombinant edges.
(B) A genomic region of size 100 base pairs with subregions affected by the
three recombinant edges. Genomic positions are evenly marked by ticks every 
10-th base pair. Local gene trees induced by the recombinant tree are
illustrated for each region covered by some combinations of recombinant edges
along the genomic region (C-G). For example, the local gene tree (E) is created
by all of the three recombinant edges in the subregion between 51 base pairs
and 70 base pairs.
We first describe procedures of summarizing recombinant trees from the first
viewpoint.  To summarize the posterior samples of \texttt{ClonalOrigin} we
examined the distribution of topologies of local genealogies induced by the
sampled recombinant trees. Recall that a recombinant tree induces a local
genealogy for each site along the analyzed block.  Figure \ref{fig:clonalorigin}
shows six local gene trees including one that is the same as the species tree
from the most left-hand side of the block of 100 base pairs to the right.  We
expected the dominant topology across sampled genealogies to be concordant with
that of the species tree. However, other frequently sampled topologies were
expected to be potentially informative about common recombination events. There
are 105 possible rooted topologies relating five taxa, which allowed us to count
topologies induced by a posterior sample of recombinant trees.  
For the second viewpoint of recombinant trees \citet{Didelot2010} suggested an
approach used to trace recombination intensity along the genome.  For each edge
type and each site, we recorded the sampling frequency of a recombinant edge of
the type at that site (e.g., Figure S\ref{fig:muts}).  Figure
\ref{fig:clonalorigin}B illustrates the posterior probability that a site
experiences influx from a donor branch using a single recombinant tree.  Summing
these posteriors over a certain set of edge types, we could obtain a measure of
recombination intensity along the genome (Figure \ref{fig:clonalorigin}B).  
}
\end{figure}
\clearpage{}%
%=============================================================================

%=============================================================================
% Figure S6: View of UCSC genome browser for bacterial gene transfer.
\begin{figure}
\includegraphics[scale=0.8]{figures/ucsc}
\caption{\label{fig:muts}Posterior probability of recombinant edges on 
aspartyl-tRNA
synthetase.  The
top line represents a genomic location of the current view in SPY1 genome. Locus
tags are represented below. The start of a locus tag is red colored, and the end
blue colored. Each of nine horizontal bars represents a branch of the five
species tree. The species tree branch is a recipient species.
The red area on SDE1 line represents gene fragment transfer from
SPY1 due to recombination in locus SpyM3\_1814 of aspartyl-tRNA synthetase.}
\end{figure}
\clearpage{}%
%=============================================================================

@@

%=============================================================================
% Figure S9:
\begin{figure}
\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R}}
\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R-inset}}

\subfloat[]{\includegraphics[scale=0.5]{figures/h2-R-inset2}}

@@

% Figure S8: recombination heatmap from mowgli
%=============================================================================
% FIGURE - Transfer heatmap
\begin{figure}
\begin{center}
% \includegraphics[width=5in]{figures/trans-recomb-heatmap}
\includegraphics[scale=0.45]{figures/heatmap-recedge-mowgli}
\end{center}
\caption{Distribution of recombining horizontal gene transfers.}
\label{fig:mowgli-recomb-heatmap}
\end{figure}
\clearpage{}
%=============================================================================
